Memo of meeting

### 2018-07-16 paper/Chapters/Chapter2.tex
strategy added

@@

>>>>

\subsection{Definition of carbohydrate intake during the survey}

@@

\section{Strategy}

To identify the best-fitting model, we used the following sequential modelling strategy \parencite{henry2010multilevel}:

\begin{itemize}
	\item Firstly, we ignored the multilevel structure of the data and estimated a series of traditional LC models to determine the number of classes at the observational-level;
	\item Next, a series of MLCA models were fitted to account for the multi-level structrure of the data. In these models, the number of observational-level classes was based on the best fitting LCA model from the first step, and the LCA model at the individual-level was estimated to identify the number of individual-level latent classes;
	\item Thirdly, when number of individual-level latent classes is defined based on the previous stage, observational-level classes was modified (one class lower and one class higher than in the second step), to see the effect of changing level 1 classes and confirm the best fitting model.
\end{itemize}
